Timeliness of security updates for Android

### 2014-11-12 securityupdates.tex
Minor tweaks to the threat model.

% Android, Unix, adb
% update, release, patch: what do we actually mean and what relevance does that have to security?
% Device manufacturers
% Network operators

@@

Secondly, support for dynamic code loading on Android means malicious code can be injected directly into existing apps installed on the handset. 
For example, the addJavascriptInterface vulnerability (CVE-2012-6636) allows Javascript running in an Android WebView to execute arbitrary code in the same process address space as the vulnerable app.
This attack works if: (1) the WebView has the Javascript-to-Java bridge enabled; and (2) the attacker is able to inject a malicious Javascript payload into the network traffic between the phone and the web server. Many apps are vulnerable to this type of attack because ad networks typically embed adverts into apps by displaying HTML and Javascript inside a WebView with the Javascript-to-Java bridge enabled. The fix for the addJavascriptInterface vulnerability breaks backwards compatibility. Therefore apps are only immune to this attack if their target API level is greater than 16 and are running on Android version 4.2 or greater.

@@

In Figure~\ref{fig:update_ecosystem} the number of updates received by devices (\daNumFullVersions) is the number of different full version strings observed in \da.
The number of updates shipped by Google (\daNumSigOSVersions) is the number of Android versions reported in \da\ which affected more than \daSigVersionPerc\ of devices for more than \daSigVersionDays\ days. \todolater{this is the wrong number to be using}

@@

\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/da_norm_os}
 \caption{Android versions in \da\ data over time}
 \label{fig:norm_os}
\end{figure}

@@

\subsubsection{Results}
\begin{figure}
 \centering
 \begin{subfigure}[b]{\columnwidth}
  \includegraphics[width=\columnwidth]{figures/device-data-all-os}
  \caption{OS versions over time. Black vertical lines indicate that the build number changed without changing the OS version at that point.}
  \label{fig:device_data_os}
 \end{subfigure}
 \begin{subfigure}[b]{\columnwidth}
  \includegraphics[width=\columnwidth]{figures/device-data-all-security}
  \caption{Number of vulnerabilities affecting each device over time}
  \label{fig:device_data_security}
 \end{subfigure}
 \caption{The top \daNumDeviceDataDevices\ devices by days of contribution in the \da\ data. One strip per device.}
\end{figure}
The longitudinal data on the number of vulnerabilities affecting the \daNumDeviceDataDevices\ devices which have contributed the most days of data to \da\ changes over time is shown in Figure~\ref{fig:device_data_security}.
The trend that we saw in Figure~\ref{fig:proportioninsecure} of security improving and then getting worse is also shown here.
It shows how some devices had vulnerabilities, which were fixed, and then further vulnerabilities were discovered, and for these devices, mostly not fixed.
This implies that these devices had been abandoned by the device manufacturer and were not receiving updates which is confirmed by Figure~\ref{fig:device_data_os} which shows which OS versions those devices were running.
Some devices start off in 2011 exposed to known security vulnerabilities and are still exposed to those and additional ones in 2014.

>>>>

% Android, Unix, adb
% update, release, patch: what do we actually mean and what relevance does that have to security?
% Device manufacturers
% Network operators
% Device model TODO check
% Device handset TODO check

@@

Secondly, support for dynamic code loading on Android means malicious code can be injected directly into existing apps installed on the handset. 
For example, the addJavascriptInterface vulnerability (CVE-2012-6636) allows Javascript running in an Android WebView to execute arbitrary code in the same process address space as the vulnerable app.
This attack works if: (1) the WebView has the Javascript-to-Java bridge enabled; and (2) the attacker is able to inject a malicious Javascript payload into the network traffic between the phone and the web server. Many apps are vulnerable to this type of attack because ad networks typically embed adverts into apps by displaying HTML and Javascript inside a WebView with the Javascript-to-Java bridge enabled. The fix for the addJavascriptInterface vulnerability breaks backwards compatibility, and therefore apps are only immune to this attack if their target API level is greater than 16 and they are running on an Android device with an OS version of 4.2 or greater.

@@

In Figure~\ref{fig:update_ecosystem} the number of updates received by devices (\daNumFullVersions) is the number of different full version strings observed in \da.
The number of updates shipped by Google (\daNumSigOSVersions) is the number of Android versions reported in \da\ which affected more than \daSigVersionPerc\ of devices for more than \daSigVersionDays\ days.
This significance test is to remove spurious versions recorded in \da\ such as `5.2.0' in 2012 which has still not been released in 2014.

@@

\begin{figure*}
 \centering
 \includegraphics[width=\textwidth]{figures/da_norm_os}
 \caption{Android versions in \da\ data over time}
 \label{fig:norm_os}
\end{figure*}

@@

\subsubsection{Results}
\begin{figure}
 \centering
 \begin{subfigure}[b]{\columnwidth}
  \includegraphics[width=\columnwidth]{figures/device-data-all-os}
  \caption{OS versions over time. Black vertical lines indicate that the build number changed without changing the OS version at that point.}
  \label{fig:device_data_os}
 \end{subfigure}
 \begin{subfigure}[b]{\columnwidth}
  \includegraphics[width=\columnwidth]{figures/device-data-all-security}
  \caption{Number of vulnerabilities affecting each device over time}
  \label{fig:device_data_security}
 \end{subfigure}
 \caption{The top \daNumDeviceDataDevices\ devices by days of contribution in the \da\ data. One strip per device handset.}
\end{figure}
The longitudinal data on the number of vulnerabilities affecting the \daNumDeviceDataDevices\ devices which have contributed the most days of data to \da\ changes over time is shown in Figure~\ref{fig:device_data_security}.
The trend that we saw in Figure~\ref{fig:proportioninsecure} of security improving and then getting worse is also shown here.
It shows how some devices had vulnerabilities, which were fixed, and then further vulnerabilities were discovered, and for these devices, mostly not fixed.
This implies that these devices had been abandoned by the device manufacturer and were not receiving updates which is confirmed by Figure~\ref{fig:device_data_os} which shows which OS versions those devices were running.
Some devices start off in 2011 exposed to known security vulnerabilities and are still exposed to those and additional ones in 2014.
